Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-21 chap-intro.tex
WIP state main thesis

\section{This thesis}
To reduce the need for manual optimizations, in this thesis we propose
techniques for optimizing collection queries and executing them
incrementally.

>>>>

\section{This thesis}
To reduce the need for manual optimizations, in this thesis we propose
techniques for optimizing higher-order collection queries and executing them
incrementally.
\pg{WIP: What's my thesis? ``We provide approaches'' is better but not yet enough.}
By generalizing database-inspired approaches, we provide approaches to query optimization and
incrementalization by code transformation to apply to higher-order collection
queries including user-defined functions.
%While
\pg{Status: others have done much more on optimization.}
Instead of building on existing approaches to incrementalization, such as
self-adjusting computation~\citep{Acar09}, we introduce a novel
incrementalization approach which enables further transformations on the
incrementalization results.
%
Further research is needed, but a number of case studies suggest at least some
limited applicability, which improves in some ways on the applicability of similar
techniques~\citep{Koch2016incremental}.
